Bayesian Nonparametric System Reliability\\ using Sets of Priors

### 2016-07-01 answer-to-reviewers.tex

\begin{frontmatter}
\title{Answer to Reviewers' Comments on our Manuscript ``Bayesian Nonparametric System Reliability\\ using Sets of Priors''}

\author[ein]{Gero Walter}
\ead{g.m.walter@tue.nl}
\author[oxf]{Louis J.M. Aslett}
\ead{louis.aslett@stats.ox.ac.uk}
\author[dur]{Frank P.A. Coolen}
\ead{frank.coolen@durham.ac.uk}

\address[ein]{School of Industrial Engineering, Eindhoven University of Technology, Eindhoven, NL}
\address[oxf]{Department of Statistics, University of Oxford, Oxford, UK}
\address[dur]{Department of Mathematical Sciences, Durham University, Durham, UK}

\begin{abstract}
We would like to thank the two anonymous reviewers for their positive and constructive feedback,
which has helped us to improve presentation in a number of crucial points, and hope that with these changes,
the manuscript can be considered for publication.

The reviewers' comments are reproduced below, with our answers interlaced. Our answers are printed in \emph{italic}.
\end{abstract}
\end{frontmatter}

@@

* P19, L56: where $\to$ when

\medskip
\emph{Fixed, thanks.}
\medskip

* Figures 5,6,7: since T1,T2 always follow the same behaviour, perhaps put them only once?

\medskip
\emph{We decided to leave the figures as they are, to allow them to be interpreted on their own,
without the need to switch between different figures.
Specifically, each complete figure allows to relate any jump in the system reliability function bounds
to the corresponding jump in either of the three component reliability function bounds.}
\medskip

### 2016-07-03 answer-to-reviewers.tex

This is expected as the general task considered by the authors is probably NP-hard (e.g. it should be possible to map it somehow to an inference in a credal network, see for instance Maua' et al., JAIR 2014). Yet, I miss a deeper discussion about the values of the parameters of the problem for which a brute-force computation of $\tilde{n}$ in Eq. 10 can be avoided. The authors say that this is the case in the 'vast majority' of the time points, but this is a strong claim, which deserves a discussion.

Of course, the discussion in S6.2 and the examples in S7 are doing something in this direction, but this is not enough.

A theoretical or empirical analysis should be necessarily added to convince the reader about the practical applicability of the result.
An idea might be a non-brute-force, approximate, approach (e.g., some sampling-based inner approximation). In the discrete case, such sampling can be drastically improved by sampling only on the extreme distribution (of the convex credal sets). This is less straightforward with continuous parameter, but it should be possible to do something even in this case (and I guess some paper by Alessio Benavoli can give direction about that).

\medskip
\emph{We have added just under 3 pages of analysis with detailed graphical plots on the question of how often one has to resort to numerical optimisation in Appendix~B in a manner that should be useful in illuminating the practical applicability of the method for readers interested in applying it.
We also reran the automotive brake example and measured precisely how often the theory helps for the automotive brake example in Section~7.2.2 adding a short comment in place and more detail in the same Appendix.}\\

### 2016-07-03 ijar-npb-ms.tex
Added 3 pages of appendix on how often the theory helps. Added a few sentences in main body of paper on the same. Updated answer to reviewers on the computational aspect. New R file which generates the plots for Appendix B.

@@

\subsubsection{Automotive brake system}

@@

@@

>>>>

Appendix \ref{ap:needtoopt} provides a detailed discussion of exactly how often these bounds hold and how often one must resort to numerical optimisation.

@@

\subsubsection{Automotive brake system}
\label{sec:brakeex}

@@

In this example, the theory presented in Section \ref{sec:setsofrel} enabled avoiding numerical optimisation in 91.9\% of cases for $\lRsys(\cdot)$ and in 95.7\% of cases for $\uRsys(\cdot)$.  Further detail is in Appendix \ref{ap:needtoopt}.

@@

\section{Theory versus optimisation}
\label{ap:needtoopt}

The above theory substantially reduces the amount that numerical optimisation must be used.  Herein, we examine more carefully precisely how often the theory cannot be applied resulting in numerical optimisation being used.

Given some unknown failure probability $p$, which gives rise to the observed data $s$, the probability that Theorem 1 does not apply is
\begin{align*}
  &P(y(N+m-1)-m+1 < s < y(N+m-1)) \\
  &\qquad \qquad \qquad \qquad = \sum_{i = \lceil y(N+m-1)-m+1 \rceil}^{\lfloor y(N+m-1) \rfloor} \binom{N}{i} p^i (1-p)^{N-i}
\end{align*}
Likewise the probability that Lemma 3 does not apply is
\begin{align*}
  &P(\mathcal{L}_{\nu,\nl}(0) \lesseqgtr 1 \cap \mathcal{L}_{\nu,\nl}(m) \gtreqless 1) = \sum_{s \in \mathcal{S}} \binom{N}{s} p^s (1-p)^{N-s} \\
  &\qquad\mbox{where}\quad \mathcal{S} = \left\{ s : \frac{p(0 \mid y, \nu, m, s, N)}{p(0 \mid y, \nl, m, s, N)} \lesseqgtr 1 \cap \frac{p(m \mid y, \nu, m, s, N)}{p(m \mid y, \nl, m, s, N)} \gtreqless 1 \right\}
\end{align*}

\subsection{Some example scenarios}

With the prior value $y$ (upper or lower) fixed, the above expressions depend only on the unknown failure probability $p$, which gives rise under repeated experiments to an observed number of failures, $s$.

\begin{figure}
\includegraphics[width=\textwidth]{need-to-opt-1}
\caption{Plots of the probability that numerical optimisation is required when $N=100$, $m=3$, $\nl=1$ and $\nu=5$ for changing choices of prior, $y$, as a function of the unknown failure probability, $p$.}
\label{fig:need-to-opt-1}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{need-to-opt-2}
\caption{Plots of the probability that numerical optimisation is required when $y=0.1$, $m=3$, $\nl=1$ and $\nu=5$ for changing amounts of test data, $N$, as a function of the unknown failure probability, $p$.}
\label{fig:need-to-opt-2}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{need-to-opt-3}
\caption{Plots of the probability that numerical optimisation is required when $y=0.4$, $N=100$, $\nl=1$ and $\nu=5$ for differing numbers of component in the system, $m$, as a function of the unknown failure probability, $p$.}
\label{fig:need-to-opt-3}
\end{figure}

Thus, Figures \ref{fig:need-to-opt-1}, \ref{fig:need-to-opt-2} and \ref{fig:need-to-opt-3} show under long term repeated use of this technique how often optimisation would be required.

The worst case scenario is that the prior, $y$, is exactly equal to the true unknown probability of failure, $p$.  Regardless of $y$, optimisation is required less frequently with larger test dataset sizes (increasing $N$), but offset by increasing numbers of the same component in a system (increasing $m$).  Not shown is that $\nl$ and $\nu$ clearly do not affect the probability that Theorem 2 does not apply, but also the impact on Lemma 3 is negligible.

\subsection{Worst case scenario}

Clearly the true failure probability, $p$, is unknown.  Figure \ref{fig:need-to-opt-45} therefore shows the worst case scenario for choice of $y$ --- that is, where the maximum of each curve from the previous subsection is taken.

\begin{figure}
\includegraphics[width=0.5\textwidth]{need-to-opt-4}\includegraphics[width=0.5\textwidth]{need-to-opt-5}
\caption{Plots of the worst case probability that numerical optimisation is required for different choices of $y$, when $m=3$ (left), $N=100$ (right), $\nl=1$ and $\nu=5$.  There are some artefacts due to the underlying discrete Binomial probabilities.}
\label{fig:need-to-opt-45}
\end{figure}

Especially given the upper and lower choices of $y$, it may be reasonable to suppose that it is unlikely that the prior probability will all that often exactly equal the true failure probability (at least not for long stretches of time).  Therefore, a final pair of plots replicates the analysis in Figure \ref{fig:need-to-opt-45}, but where the worst case $p$ is subject to the constraint $|y-p|>0.1$.  This is shown in Figure \ref{fig:need-to-opt-67}

\begin{figure}
\includegraphics[width=0.5\textwidth]{need-to-opt-6}\includegraphics[width=0.5\textwidth]{need-to-opt-7}
\caption{Plots of the worst case probability that numerical optimisation is required for different choices of $y$, when $m=3$ (left), $N=100$ (right), $\nl=1$ and $\nu=5$, subject to the constraint $|y-p|>0.1$.  There are some artefacts due to the underlying discrete Binomial probabilities.}
\label{fig:need-to-opt-67}
\end{figure}

Note that all these analyses are for evaluation of a single fixed time point at which $\lRsys(\cdot)$ or $\uRsys(\cdot)$ computed.  Of relevance to the overall compute time is the behaviour over time, so that is seems unlikely the worst case scenario will be occur for long runs of the times under analysis.

\subsection{Theoretical analysis for brake system example}

By way of example, a temporal analysis of the constrained worst case analysis is now presented for the real example in Section \ref{sec:brakeex}.

Figure \ref{fig:need-to-opt-8} shows the changing worst case probability (subject to $|y-p|>0.1$) that optimisation will be required over time for the actual choice of prior and the values of $m, N, \nu$ and $\nl$ in the brake example from the main body of the paper.  Note in particular that when $m=1$, Lemma 3 is always applies and optimisation is never required.  This is true for all values of $N$ and $y$.

\begin{figure}
\includegraphics[width=\textwidth]{need-to-opt-8}
\caption{Plots of the worst case probability that numerical optimisation is required over time in the brake example, subject to the constraint $|y-p|>0.1$.}
\label{fig:need-to-opt-8}
\end{figure}

As explained in section \ref{sec:brakeex}, the grid contained 301 time points and the system has 4 types of component, meaning a stochastic dominance must be verified via theory or optimisation $1,204$ times for each of $\lRsys(\cdot)$ and $\uRsys(\cdot)$.  In total, theory could not determine stochastic dominance in 98 (or 8.1\%) of cases for $\lRsys(\cdot)$, while it was in 52 (or 4.3\%) of cases for $\uRsys(\cdot)$.
